Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-09 article/article.tex
Commit 2024-06-09 20:15

The above clear sky reference values are based on the climatological AOD
and WC, hence they cannot describe accurately the long term variation of
\(\text{GHI}_\text{ref}\) due to changes in the two atmospheric
constituents, mainly AOD. As reported by \citet{Natsis2023}, there is a
long term brightening effect in the GHI data of Thessaloniki for the
period 1993 -- 2023, which for clear-sky data was attributed to
long-term changes in aerosol effects. In order to better incorporate
this change, we used, estimations of AOD change derived from two
sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
spectrophotometer. For 2005 to 2023, we derived the trend from the
available monthly climatological data of AERONET.

>>>>

The above clear sky reference values are not enough to describe the long
term variation, due to the changes of the atmospheric constituents,
mainly AOD. As observed by \citet{Natsis2023}, there is a long term
brightening effect, over Thessaloniki for the studied period. In order
to better incorporate this change, we used, estimations of AOD change
derived from two sources. For 1993 -- 2005, \citet{Kazadzis2007} have
found a change of \(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\),
using a Brewer spectrophotometer. For 2005 to 2023, we derived the trend
from the available monthly climatological data of AERONET.
